\documentclass[10pt, letterpaper]{article}

\usepackage{cv}
\usepackage{ifthen}
\newcommand{\entryspacing}{0.20 cm}
\newboolean{for_website}
\setboolean{for_website}{false}
\newboolean{no_links}
\setboolean{no_links}{false}

\ifthenelse{\equal{\jobname}{\detokenize{website}}}{\setboolean{for_website}{true}}{\setboolean{for_website}{false}}
\ifthenelse{\equal{\jobname}{\detokenize{nolinks}}}{\setboolean{no_links}{true}}{\setboolean{no_links}{false}}

\usepackage{xcolor}
\newcommand{\updateinfo}[1][\today]{%
    \par\vfill\hfill{\scriptsize\color{gray}Last updated on #1} \vspace{-24pt}
}

\newcommand{\headerand}{%
    \kern 5.0 pt%
    |%
    \kern 5.0 pt
}
\newcommand{\headerhref}[2]{\mbox{\hrefWithoutArrow{#1}{#2}}}

\begin{document}

\ifthenelse{\boolean{for_website}}{\updateinfo[Jun 4th, 2026]}{}

\ifthenelse{\boolean{no_links}}{\begin{NoHyper}}{}

\begin{header}
    \fontsize{25 pt}{25 pt}\selectfont Ben M.\ Andrew

    \vspace{5 pt}

    \normalsize
    \headerhref{mailto:benjamin.andrew@manchester.ac.uk}{benjamin.andrew@manchester.ac.uk}%
    \headerand%
    \headerhref{http://benmandrew.com/}{benmandrew.com}%
    \ifthenelse{\boolean{no_links}}{}{%
    \headerand%
    \headerhref{https://linkedin.com/in/benmandrew}{linkedin.com}%
    \headerand%
    \headerhref{https://github.com/benmandrew}{github.com}%
    }
\end{header}

\vspace{5 pt - 0.3 cm}

\section{Education}

    \begin{cventry}{Sep 2024 -- Present}{\textbf{University of Manchester}, PhD in Computer Science}
        \item Research focused on formal methods for understanding degraded systems.
        \item Supervised by \href{https://mariefarrell.github.io/}{Dr.~Marie Farrell}, \href{https://personalpages.manchester.ac.uk/staff/louise.dennis/}{Dr.~Louise Dennis}, and \href{https://personalpages.manchester.ac.uk/staff/michael.fisher/}{Prof.~Michael Fisher}.
    \end{cventry}

    \vspace{\entryspacing}

    \begin{cventry}{Oct 2019 -- Jun 2022}{\textbf{University of Cambridge}, BA (Hons) in Computer Science}
        \item Grade II.1 (70\%).
        \item Dissertation titled \textit{Delay-Tolerant Link-State Routing}. Implemented and empirically evaluated a failure-tolerant routing protocol in C to run on real Unix-based routers, comparing with traditional protocols. Supervised by \href{https://jacksonwoodruff.com/}{Dr.~Jackson Woodruff}.
    \end{cventry}

\section{Publications}

    \begin{onecolentry}
        \begin{highlights}
        \item Andrew, B.\,M., Dennis, L.\,A., Fisher, M., Farrell, M. \textit{Counterexample-Guided Interval Weakening}. Rigorous State-Based Methods (ABZ) 2026. \hrefWithoutArrow{https://doi.org/10.1007/978-3-032-26752-8_1}{10.1007/978-3-032-26752-8\_1}
        \end{highlights}
    \end{onecolentry}

    \vspace{\entryspacing}

    \begin{onecolentry}
        \begin{highlights}
        \item Andrew, B.\,M. \textit{Weakening Goals in Logical Specifications}. Rigorous State-Based Methods (ABZ) 2025. \hrefWithoutArrow{https://doi.org/10.1007/978-3-031-94533-5_22}{10.1007/978-3-031-94533-5\_22}
        \end{highlights}
    \end{onecolentry}

\section{Industry Experience}

    \begin{cventry}{Sep 2022 -- Jun 2024}{\textbf{Software Engineer}, Tarides -- Paris, France}
        \item Developed open-source continuous integration (CI) software for the OCaml language's ecosystem, involving systems programming to distribute dependency solving, compilation, and testing to many operating systems and architectures.
        \item Responsible for the CI of the Opam Repository, the central package universe for OCaml with tens of thousands of packages.
    \end{cventry}

    \vspace{\entryspacing}

    \begin{cventry}{Jul -- Sep 2021}{\textbf{Embedded Systems Intern}, Tarides -- Paris, France}
        \item Research \& development project to cross-compile the OCaml bytecode runtime to an ARM-based microcontroller using a real-time operating system as a base layer.
    \end{cventry}

    \vspace{\entryspacing}

    \begin{cventry}{Jun -- Sep 2020}{\textbf{Computer Graphics Research Intern}, University of Cambridge}
        \item Developed and implemented a visual model of ageing vision in virtual reality with Unity, as part of the Graphics and Displays Research Group.
    \end{cventry}

\section{Professional Activities}
\begin{onecolentry}
    \begin{highlights}
        \item Part of the local organising committee of Integrated Formal Methods (iFM) 2024.
        \item Member of the \hrefWithoutArrow{https://autonomy-and-verification.github.io}{Autonomy and Verification Network}.
    \end{highlights}
\end{onecolentry}

\section{Teaching Experience}

    \begin{cventry}{Oct 2022 -- Present}{\textbf{University of Cambridge}, Supervisor (TA equiv.)}
        \item Leading small group supervisions for undergraduate courses in computer science, including topics such as logic, formal verification, and semantics of programming languages.
    \end{cventry}

    \vspace{\entryspacing}

    \begin{cventry}{Oct 2024 -- May 2026}{\textbf{University of Manchester}, Graduate Teaching Assistant}
        \item Assisting in teaching graduate and undergraduate courses in computer science, including topics such as software engineering, logic, and formal verification.
    \end{cventry}

\section{Volunteering}

    \begin{cventry}{Dec 2024 -- Present}{\textbf{Run Leader}, Runwild -- University of Manchester}
        \item Lead bi-weekly group runs for a student running group.
    \end{cventry}

    \vspace{\entryspacing}

    \begin{cventry}{Jul -- Aug 2024}{\textbf{English Teacher}, Connections English Institute -- Ibagué, Colombia}
        \item Taught adult beginners in morning and night classes.
    \end{cventry}

\ifthenelse{\boolean{no_links}}{\end{NoHyper}}{}

\end{document}
